Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-25 prop_iop.tex
prop_iop.tex \subsubsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $1/n$.
For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{lemma}

\begin{proof}By definition, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
for all $P\in\events$. By substitute $P=\proj{\psi}$, we have 
\begin{equation}
\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)\,.\label{eq:consistent2another_state}
\end{equation}
Since the maximum length of intervals in $\mathscr{I}$ is $1/n$,
we can move $\rho$ and $\rho'$ to the same side and rewrite equation~(\ref{eq:consistent2another_state})
as
\begin{equation}
\frac{1}{n}\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
\end{equation}
Applying maximum on both side, we have
\begin{equation}
\frac{1}{n}\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
\end{equation}
\end{proof}

@@

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the minimum length of intervals in $\mathscr{I}\backslash\left\{ \imposs,\necess\right\} $
is $1/n$. For two mixed state\nb$\rho$ and $\rho'$, if the following
conditions holds.
\begin{itemize}
\item $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\imposs$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\necess$ if and only if $P=\mathbb{1}$.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

\begin{proof}Since
\begin{equation}
\frac{1}{n}\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
\frac{1}{n}\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|
\end{equation}
for all normalized pure state\nb$\ket{\psi}$. \end{proof}

>>>>

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}

\begin{proof}By definition, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$
for all $P\in\events$. By substitute $P=\proj{\psi}$, we have 
\begin{equation}
\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right)\,.\label{eq:consistent2another_state}
\end{equation}
Since the maximum length of intervals in $\mathscr{I}$ is $\delta$,
we can move $\rho$ and $\rho'$ to the same side and rewrite equation~(\ref{eq:consistent2another_state})
as
\begin{equation}
\delta\ge\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|=\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,.
\end{equation}
Applying maximum on both side, we have
\begin{equation}
\delta\ge\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left\Vert \rho'-\rho\right\Vert \,.
\end{equation}
\end{proof}

@@

\begin{lemma}Given a $d$-dimensional Hilbert space with the set
of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
holds.
\begin{itemize}
\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
\item $\left\Vert \rho-\rho'\right\Vert \le d\delta$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=0$ if and only if $P=\mathbb{0}$.
\item $\mu_{\rho}^{\mathrm{B}}\left(P\right)=1$ if and only if $P=\mathbb{1}$.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

\begin{proof}Since
\begin{equation}
d\delta\ge\left\Vert \rho'-\rho\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho'-\rho}{\psi}\right|\,,
\end{equation}
we have
\begin{equation}
d\delta\ge\left|\melem{\psi}{\rho'-\rho}{\psi}\right|=\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)\right|\label{eq:Born_rule_difference}
\end{equation}
for all normalized pure state\nb$\ket{\psi}$.

When $P\in\left\{ \mathbb{0},\mathbb{1}\right\} $, it is obvious
$\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.

When $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $,
there exists an orthonormal set $\left\{ \ket{i}\right\} _{i=0}^{d'-1}$
such that $P=\sum_{i=0}^{d'-1}\proj{i}$. By applying equation~(\ref{eq:Born_rule_difference}),
\begin{equation}
\left|\mu_{\rho'}^{\mathrm{B}}\left(P\right)-\mu_{\rho}^{\mathrm{B}}\left(P\right)\right|\le\sum_{i=0}^{d'-1}\left|\mu_{\rho'}^{\mathrm{B}}\left(\proj{i}\right)-\mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)\right|\le\delta\,.
\end{equation}

Since $P$ is neither $\mathbb{0}$ nor $\mathbb{1}$, $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\left(0,1\right)$.
Hence, we have $\mu_{\rho'}^{\mathrm{B}}\left(P\right)\in\iota\left(\mu_{\rho}^{\mathrm{B}}\left(P\right)\right)$.\end{proof}
